---
title: "Aggregate Correspondence Table"
output:
  rmarkdown::html_vignette:
    toc: TRUE
vignette: >
  %\VignetteIndexEntry{Aggregate Correspondence Table}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}  
---
    


```{r setup, include=FALSE}

knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  cache = FALSE
)

```

## Overview

This vignette demonstrates how to use the aggregateCorrespondenceTable() function from the correspondenceTables package.
The function aggregates numeric values expressed in a source classification (A) into a target classification (B), using a correspondence table that links A to B (denoted A → B).
When correspondence weights are available, values are redistributed proportionally according to these weights.
If no weights are provided, values are split equally across the corresponding target codes.
This type of aggregation is commonly used to convert statistics between classification systems, for example:

NACE → CPA

CPA → CN

PRODCOM → CPA

CPC → HS

Load the package correspondenceTables: 
```{r cars}
library(correspondenceTables)
```


**Inputs** 

The aggregateCorrespondenceTable() function expects the following inputs:

**AB**
A data frame representing the correspondence table between classification A and classification B.
It must contain at least:

a source code column (from_code)
a target code column (to_code)
optionally, a weight column

**A**
A data frame containing values expressed in the source classification A.
This typically includes:

a source classification code
one or more numeric variables to be aggregated

**B (optional)**
A data frame defining the domain of the target classification B.
If provided, all B codes are preserved in the output; target codes with no matching contributions receive a value of zero.
 
 
## **Application of the aggregateCorrespondenceTable()**

### **Example 1: Basic aggregation using a correspondence table**

In this example, all inputs are read from sample datasets included in the package.


```{r}
AB_path <- system.file("extdata", "ab_data.csv", package = "correspondenceTables")
A_path  <- system.file("extdata", "a_data.csv",  package = "correspondenceTables")
B_path  <- system.file("extdata", "b_data.csv",  package = "correspondenceTables")

stopifnot(nzchar(AB_path), nzchar(A_path), nzchar(B_path))

AB <- utils::read.csv(AB_path, stringsAsFactors = FALSE)
A  <- utils::read.csv(A_path,  stringsAsFactors = FALSE)
B  <- utils::read.csv(B_path,  stringsAsFactors = FALSE)

#For clarity and consistency, the correspondence table columns are renamed to the expected identifiers:

names(AB)[names(AB) == "NACE.Rev..2.Code"]   <- "from_code"
names(AB)[names(AB) == "NACE.Rev..2.1.Code"] <- "to_code"

#<- "to_code"Show more lines

res <- aggregateCorrespondenceTable(AB = AB, A = A, B = B)


knitr::kable(
  head(res$result),
  caption = "Aggregation using a correspondence table",
  align = "lll"
)

```

The returned object is a list.
The aggregated values are stored in the result element, which is a data frame structured according to the target classification B.

**Notes**

If a source code maps to multiple target codes, values are split according to the correspondence weights.
If no weights are supplied, equal splitting is applied.
Supplying the B argument ensures that the output covers the full target classification domain, even for codes with zero contributions.


### **Example 2: Weighted correspondence (proportional allocation)**
This example shows how values from A are redistributed to B using explicit weights.  

```{r}

 # Correspondence table with weights
AB <- data.frame(
  from_code = c("A1", "A1", "A2"),
  to_code   = c("B1", "B2", "B2"),
  weight    = c(0.7, 0.3, 1.0)
)

# Source classification with values  
A <- data.frame(
  code  = c("A1", "A2"),
  value = c(100, 50)
)

# Target classification domain
B <- data.frame(
  code = c("B1", "B2")
)

res2 <- aggregateCorrespondenceTable(AB = AB, A = A, B = B) 



knitr::kable(
  head(res2$result),
  caption = "Weighted correspondence (proportional allocation)",
  align = "lll"
)



```

