---
title: "AnalyseCorrespondenceTable"
description: "This vignette explains how to use the analyseCorrespondenceTable function."
vignette: >
  %\VignetteIndexEntry{Analyse classification correspondence tables with the correspondenceTables package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Description

This vignette explains how to use the `analyseCorrespondenceTable` function to perform analysis on correspondence tables.

### Package Installation

To use the `analyseCorrespondenceTable` function, you first need to install and load the `correspondenceTables` package. You can use the following command:

```{r include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

```{r}
library(correspondenceTables)
```

```{r results='hide'}
# Perform analysis
result <- analyseCorrespondenceTable(AB =system.file("extdata", "ExempleAnnexe.csv", package = "correspondenceTables")
                                     , A = NULL, formatA = NULL, B = NULL, formatB = NULL,
                                     CSVcorrespondenceInventory =system.file("extdata", "CorrespondenceInventoryExample.csv", package = "correspondenceTables"), CSVcorrespondenceAnalysis = system.file("extdata", "CorrespondenceAnalysisExample.csv", package = "correspondenceTables"))

# Print the results
print(result$Annexe_A)
print(result$Annexe_B)

```

For this example we use output  **CSVcorrespondenceInventory** **CSVcorrespondenceAnalysis** are not NULL. 
Indeed we put our output in these csv files and we can see these with the both print on this function.


**Another example**

Here we use all the function parameters. 

We'll see what happens with AB, which contains data from nace2 & nace2.1. 

A which contains Nace2 as a classification source 

B which contains Nace2.1 as the classification target 

formatA format B will have a numeric value of 1 and 5 here to have the first position and the last position at the lowest level. 

```{r}
result2 <-analyseCorrespondenceTable(AB = (system.file("extdata", "ab_data.csv", package = "correspondenceTables")),
                             A =  (system.file("extdata", "a_data.csv", package = "correspondenceTables")) ,
                             formatA = c(1,5) ,
                             B = B <- (system.file("extdata", "b_data.csv", package = "correspondenceTables")),
                             formatB = c(1,5),
                             CSVcorrespondenceInventory = T, CSVcorrespondenceAnalysis = T)

print(result2$Annexe_A)
###for Annexe_A run this code : View(result2$Annexe_A)
print(result2$Annexe_B)
```


