---
title: "Analyse Correspondence Table"
description: This vignette explains how to use the analyseCorrespondenceTable function.
vignette: "%\\VignetteIndexEntry{Analyse classification correspondence tables with
  the correspondenceTables package} %\\VignetteEngine{knitr::rmarkdown} %\\VignetteEncoding{UTF-8}\n"
---

## Description

This vignette explains how to use the `analyseCorrespondenceTable` function to perform analysis on correspondence tables.

### Package Installation

To use the `analyseCorrespondenceTable` function, you first need to install and load the `correspondenceTables` package. You can use the following command:

```{r include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

```{r}
library(correspondenceTables)
```

```{r results='hide'}
# Perform analysis
result <- analyseCorrespondenceTable(AB =system.file("extdata", "ExempleAnnexe.csv", package = "correspondenceTables")
                                     , A = NULL, longestAcodeOnly = FALSE, B = NULL, longestBcodeOnly = FALSE,
                                     CSVcorrespondenceInventory = NULL, CSVcorrespondenceAnalysis = NULL)



# Print the results
print(result$Inventory)
print(result$Analysis)

```

For this example we use output  **CSVcorrespondenceInventory** **CSVcorrespondenceAnalysis** are not NULL. 
Indeed we put our output in these csv files and we can see these with the both print on this function.


**Another example**

Here we use all the function parameters. 

We'll see what happens with AB, which contains data from nace2 & nace2.1. 

A which contains Nace2 as a classification source 

B which contains Nace2.1 as the classification target 

longestAcodeOnly and longestBcodeOnly will be set to TRUE here to have only the retain only the lowest level. 

```{r}
result2 <-analyseCorrespondenceTable(AB = system.file("extdata", "ExempleAnnexe.csv", package = "correspondenceTables"), A =  NULL , longestAcodeOnly = FALSE ,
                             B = NULL,
                             longestBcodeOnly = FALSE, CSVcorrespondenceInventory = NULL, CSVcorrespondenceAnalysis = NULL)

print(result2$Inventory)
###for Inventory run this code : View(result2$Inventory)
print(result2$Analysis)
```


