---
title: "Analyse Correspondence Table"
output:
  rmarkdown::html_vignette:  
    toc: TRUE
description: "This vignette explains how to use the analyseCorrespondenceTable function."
vignette: >
  %\VignetteIndexEntry{Analyse Correspondence Table}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```


## Overview
This vignette demonstrates how to use the analyseCorrespondenceTable() function from the correspondenceTables package to analyse classification correspondence tables.
The function provides diagnostic information on the structure and quality of a correspondence table, such as:


* the inventory of codes involved on both sides of the correspondence;
* the presence of one‑to‑one, one‑to‑many, or many‑to‑many relationships;
* potential structural issues that may affect downstream use (aggregation, updates, or quality checks).


Load the package correspondenceTables: 
```{r}
library(correspondenceTables)  
```

## Application of analyseCorrespondenceTable

### **Example 1: Basic analysis of a correspondence table**
In this first example, only a correspondence table is provided.
No explicit source or target classification tables are supplied.


```{r}
# Load example correspondence table
AB <- read.csv(
  system.file("extdata", "ExempleAnnexe.csv", package = "correspondenceTables"),
  stringsAsFactors = FALSE
)

```


The analysis is then performed using default settings:


```{r}
# Perform analysis
result <- analyseCorrespondenceTable(
  AB = AB,
  A  = NULL,
  B  = NULL,
  longestAcodeOnly = FALSE,
  longestBcodeOnly = FALSE
)
#head(result$Inventory)
#head(result$Analysis)
```

The function returns a list containing multiple outputs.
Two key components are displayed below:

```{r}
# Display results

knitr::kable(
  head(result$Inventory),
  caption = "Inventory results: Basic analysis of a correspondence table",
  align = "lll"
)


knitr::kable(
  head(result$Analysis),
  caption = "Analysisresults: Basic analysis of a correspondence table",
  align = "lll"
)

```
 
In this example, both the correspondence inventory and the analytical summary
are available and printed. These outputs can be used to inspect the overall
structure of the correspondence table.


### **Example 2: Full analysis with source and target classifications**
In this second example, all supported parameters of the function are used.

AB contains a correspondence table between NACE Rev. 2 and NACE Rev. 2.1
A contains the source classification (NACE Rev. 2)
B contains the target classification (NACE Rev. 2.1)

The analysis is restricted to the lowest‑level codes on both sides of the
correspondence.
 

```{r}
# Load correspondence table (NACE Rev.2 -> NACE Rev.2.1)
AB <- read.csv(
  system.file("extdata", "ab_data.csv", package = "correspondenceTables"),
  stringsAsFactors = FALSE
)

# Load source classification (NACE Rev.2)
A <- read.csv(
  system.file("extdata", "a_data.csv", package = "correspondenceTables"),
  stringsAsFactors = FALSE
)

# Load target classification (NACE Rev.2.1)
B <- read.csv(
  system.file("extdata", "b_data.csv", package = "correspondenceTables"),
  stringsAsFactors = FALSE
)

```


```{r warning = FALSE}
# Perform analysis using all function parameters
result2 <- analyseCorrespondenceTable(
  AB = AB,
  A  = A,
  B  = B,
  longestAcodeOnly = TRUE,
  longestBcodeOnly = TRUE
)

```


The resulting inventory and analysis summary are shown below:


```{r}
# Display results

knitr::kable(
  head(result2$Inventory),
  caption = "Inventory results: Full analysis with source and target classifications",
  align = "lll"
)


knitr::kable(
  head(result2$Analysis),
  caption = "Analysis results: Full analysis with source and target classifications",
  align = "lll"
)  









```

 


Restricting the analysis to the lowest‑level codes can be useful when the
correspondence table is intended for aggregation or conversion at the most
granular classification level.


## Notes

If A and B are provided, the function can perform additional consistency checks against the source and target classification domains.
The longestAcodeOnly and longestBcodeOnly arguments allow users to focus the analysis on the most detailed codes, which is often desirable in practical statistical workflows.



