---
title: "Classification Quality Control"
output:
  rmarkdown::html_vignette:  
    toc: TRUE
vignette: >
  %\VignetteIndexEntry{Classification Quality Control}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8} 
---

```{r include=FALSE}

knitr::opts_chunk$set(
  collapse = TRUE,
  comment  = "#>",
  warning  = FALSE,
  message  = FALSE
)

```

This vignette provides information about the functions included in the correspondenceTables package used to create a quality control of the classification

```{r}
library(correspondenceTables)
```




## Overview

Classification quality control


The main function classificationQC() is designed to perform structural and logical quality control on hierarchical classifications.
It returns a list of data frames, including an enriched version of the classification (QC_output) and additional tables flagging potential issues such as orphan codes, duplicate labels, or sequencing problems.
The function takes the following arguments:

* **classification** – a data frame containing the classification codes and labels.
* **lengths** – a data frame defining the hierarchical structure of the codes using the columns charb and chare.
* **fullHierarchy** – when TRUE, the function checks both the absence of orphan codes and the absence of childless internal nodes. When FALSE, no hierarchical completeness checks are performed.
* **labelUniqueness** – when TRUE, checks that labels are unique within each hierarchical level.
* **labelHierarchy** – when TRUE, checks label consistency between parents and children.
* **singleChildCode** – an optional data frame defining admissible coding rules for single‑child and multiple‑child situations.
* **sequencing** – an optional data frame defining admissible ordering rules for multiple‑child situations.

The function does not write output files. Export to CSV must be handled explicitly by the user outside the function.

**Requirements**
The following auxiliary input files are expected when using the arguments lengths, singleChildCode, and sequencing.

**lengths**
The user provides a data frame with the headers **charb and chare**.
If these headers are missing or incorrect, the function issues a warning and automatically renames the first two columns accordingly.

**singleChildCode**
The user provides a data frame with the headers **level, singleCode, and multipleCode**.
If these headers are missing or incorrect, the function issues a warning and renames the first three columns accordingly.

**sequencing**
The user provides a data frame with the headers **level and multipleCode**.
As with singleChildCode, incorrect or missing headers are automatically detected and corrected with a warning.

In the following example, the auxiliary files are loaded to illustrate how the function handles both correctly and incorrectly specified column headers.


## Auxiliary Tables for Classification Validation

The validation procedures rely on a small set of auxiliary tables that
define structural constraints such as expected code lengths, single-child
rules, and sequencing between levels.

We load three auxiliary tables used for classification validation.
Some of the raw CSV files do not use standard column names and must
therefore be normalised explicitly.


### Definition of expected code lengths by level

We first load the file defining the expected code lengths by level.
This raw file does not provide meaningful column names, so we inspect its structure before standardisation.

```{r}
lengths <- read.csv(
  system.file("extdata", "lenghtsNaceNoColumn.csv",
              package = "correspondenceTables")
)

knitr::kable(
  head(lengths, 5),
  caption = "Original lengths file (no meaningful column names)"
)
```

### Standardising column names for the lengths table

To make the table usable in validation routines, we explicitly assign semantic column names:
level for the hierarchical level and nchar for the expected code length.

```{r}
colnames(lengths) <- c("level", "nchar")

knitr::kable(
  head(lengths, 5),
  caption = "Lengths table after renaming columns"
)

```

### Single-child code constraints
The following table specifies levels where codes are expected to have a single child (or allow multiple children).
This structure is already correctly formatted and can be used as-is.


```{r}
singleChildCode <- read.csv(
  system.file("extdata", "SingleChild.csv",
              package = "correspondenceTables")
)

knitr::kable(
  singleChildCode,
  caption = "Single-child code rules"
)
```

### Sequencing rules between hierarchical levels

Finally, we normalise the sequencing table, which defines ordering constraints between levels.
Column names are adjusted to make the intended structure explicit.


```{r}

sequencing <- read.csv(
("C:/Users/mbaldacc/OneDrive - Capgemini/Projects/Correspondence Table R/updated functions/10.35/correspondenceTables-10.35/inst/extdata/Sequencing.csv")
)

# sequencing <- read.csv(
#   system.file("extdata", "Sequencing.csv",
#               package = "correspondenceTables")
# )
# 


colnames(sequencing) <- c("level", "order")


sequencing$order_short <- ifelse(
  nchar(sequencing$order) > 12,
  paste0(substr(sequencing$order, 1, 12), "..."),
  sequencing$order
)

knitr::kable(
  sequencing[, c("level", "order_short")],
  caption = "Sequencing rules (order truncated for display)"
)

```


## Example 1: Basic quality control using hierarchy definitions

The following example applies `classificationQC()` to the NACE Rev.2 classification using additional parameters

In this example, the user provides:
- a data frame containing the classification to be checked, and
- a data frame defining the hierarchical structure of the classification through the `lengths` argument.

Different parameters of the `classificationQC()` function are used to demonstrate how structural and logical quality checks are applied to the classification.


```{r}
classification <- read.csv(
  system.file("extdata", "Nace2.csv", package = "correspondenceTables")
)

lengths <- data.frame(charb = c(1,2,3,5), chare = c(1,2,4,5))

```



```{r}

output <- classificationQC(
  classification   = classification,
  lengths          = lengths,
  fullHierarchy    = TRUE,
  labelUniqueness  = TRUE,
  labelHierarchy   = TRUE,
  singleChildCode  = NULL,
  sequencing       = NULL
)

qc_summary <- data.frame(
  Check               = c("No levels", "Orphan codes", "Childless codes"),
  Number_of_issues    = c(
    nrow(output$QC_noLevels),
    nrow(output$QC_orphan),
    nrow(output$QC_childless)
  )
)

knitr::kable(
  qc_summary,
  caption = "Summary of quality control checks"
)

```




### Codes with no hierarchy level (`QC_noLevels`)

The following table lists classification codes that are missing a declared
hierarchy level. Such codes cannot be placed correctly in the classification
structure.

```{r, echo=FALSE, results="asis"}  

tbl <- output$QC_noLevels

cat(sprintf(
  "**QC_noLevels**\n\n- Rows: %d  \n- Columns: %d\n\n",
  nrow(tbl), 
  ncol(tbl)
))

```


### Orphan codes (`QC_orphan`)

Orphan codes are codes that have no parent code at a higher hierarchical level.
This usually indicates breaks in the hierarchical structure.

```{r, echo=FALSE, results="asis"}

tbl2 <- output$QC_orphan

cat(sprintf(
  "**QC_orphan**\n\n- Rows: %d  \n- Columns: %d\n\n",
  nrow(tbl2), 
  ncol(tbl2) 
))



knitr::kable(
  head(tbl2[, 1:8], 5),
  caption = "First 5 rows (first 7 columns)"
)
```

### Childless codes (`QC_childless`)  

Childless codes are codes that have no descendants at lower hierarchical levels.
This can be expected at the lowest level of a classification, but may indicate
structural issues at higher levels.


```{r, echo=FALSE, results="asis"}
tbl3 <- output$QC_childless

cat(sprintf(
  "**QC_childless**\n\n- Rows: %d  \n- Columns: %d\n\n",
 nrow(tbl3), 
 ncol(tbl3)
))

knitr::kable(
  head(tbl3[, 1:8], 5),
  caption = "First 5 rows (first 7 columns)"
)

```


**Full hierarchy**  

When `fullHierarchy = TRUE`, the function checks the completeness of the hierarchical structure by applying two rules:

- **Orphan check**:  
  A new field in the QC output, named `orphan`, takes the value 1 for positions at hierarchical level *j > 1* that lack a parent at the immediately higher level (*j − 1*), and 0 otherwise.

- **Childless check**:  
  A new field in the QC output, named `childless`, takes the value 1 for positions at hierarchical level *j < k* that lack a child at the immediately lower level (*j + 1*), and 0 otherwise.

When `fullHierarchy = FALSE`, no hierarchical completeness checks (neither orphan nor childless) are performed.

---

The **labelUniqueness** argument (default value: `TRUE`) indicates whether compliance with label uniqueness is tested.  
The test outcome is reported in a new QC output column, `duplicateLabel`, which takes the value 1 for positions involved in duplicate labels within the same hierarchical level, and 0 otherwise.

---

The **labelHierarchy** argument (default value: `TRUE`) indicates whether label consistency between parents and children is tested.  
The test outcome is reported in a new QC output column, `singleChildMismatch`, for hierarchical levels *j > 1* (with no value at the highest level):

- value **1** indicates a single child whose label does not match that of its parent;
- value **9** indicates a child whose label matches that of its parent without being a single child;
- value **0** indicates compliance.

---
## Example 2: Quality control with single‑child coding rules

The following example illustrates the quality control of the NACE Rev.2 classification from CELLAR using additional parameters, including the `singleChildCode` argument.


```{r}

singleChildCode <- read.csv(
  system.file("extdata", "SingleChild.csv", package = "correspondenceTables")
)


output2 <- classificationQC(
  classification   = classification,
  lengths          = lengths,
  fullHierarchy    = TRUE,
  labelUniqueness  = TRUE,
  labelHierarchy   = TRUE,
  singleChildCode  = singleChildCode,
  sequencing       = NULL
)


#head(output2$QC_orphan[, c("Code", "Parent", "level")])  
#head(output2$QC_noLevels)
#head(output2$QC_childless)  
```

This table lists orphan codes, i.e. codes that do not have a valid parent at the immediately higher hierarchical level.

```{r, echo=FALSE, results="asis"}
tbl4 <- output2$QC_orphan

cat(sprintf(
  "**QC_orphan**\n\n- Rows: %d  \n- Columns: %d\n\n",
  nrow(tbl4), 
  ncol(tbl4)
))


knitr::kable(
  head(tbl4[, 1:8], 5),
  caption = "First 5 rows (first 7 columns)"
)

```

This table identifies classification codes for which no hierarchical level could be determined


```{r, echo=FALSE, results="asis"}
tbl5 <- output2$QC_noLevels

cat(sprintf(
  "**QC_noLevels** \n\n- Rows: %d  \n- Columns: %d\n\n",
  nrow(tbl5), 
  ncol(tbl5)
))

```

This table lists childless codes, i.e. codes that have no descendants at the immediately lower hierarchical level

```{r, echo=FALSE, results="asis"}
tbl6 <- output2$QC_childless

cat(sprintf(
  "**QC_childless**\n\n- Rows: %d  \n- Columns: %d\n\n",
 nrow(tbl6), 
  ncol(tbl6) 
))


knitr::kable(
  head(tbl6[, 1:8], 10),
  caption = "First 10 rows (first 7 columns)"
)


```


## Example 3: Quality control with sequencing constraints

In this final example, the `sequencing` parameter is used to check the ordering of multiple children within the hierarchy.

Sequencing rules are applied at hierarchical levels 3 and 4, as specified in the `sequencing` input table.  
At these levels, the function verifies that codes corresponding to multiple children follow the expected order and flags potential gaps or inconsistencies in the sequence.


```{r}

## Example: use of sequencing at levels 3 and 4

singleChildCode <- read.csv(
  system.file("extdata", "SingleChild2.csv", package = "correspondenceTables")
)

sequencing <- data.frame(
  level = c(3, 4),
  multipleCode = c("123", "123")
)

output3 <- classificationQC(
  classification   = classification, 
  lengths          = lengths,
  fullHierarchy    = TRUE,
  labelUniqueness  = TRUE,
  labelHierarchy   = TRUE,
  singleChildCode  = singleChildCode,
  sequencing       = sequencing
)

#head(output3$QC_output)
#head(output3$QC_gapBefore)
#head(output3$QC_lastSibling)

```

This table identifies gaps in the expected sequence of sibling codes within the same parent

```{r, echo=FALSE, results="asis"}
tbl7 <- output3$QC_gapBefore

cat(sprintf(
  "**QC_gapBefore**\n\n- Rows: %d  \n- Columns: %d\n\n",
  nrow(tbl7),
  ncol(tbl7)
))

```

This table lists the last sibling codes within each group of children, used to assess sequencing completeness
 

```{r, echo=FALSE, results="asis"}  
tbl8 <- output3$QC_lastSibling

cat(sprintf(
  "**QC_lastSibling**\n\n- Rows: %d  \n- Columns: %d\n\n",
  nrow(tbl8),
  ncol(tbl8)
))


```

This table contains the full classification enriched with all quality‑control flags produced by the checks


```{r, echo=FALSE, results="asis"}
tbl9 <- output3$QC_output

cat(sprintf(
  "**QC_output**\n\n- Rows: %d  \n- Columns: %d\n\n",
  nrow(tbl9), 
  ncol(tbl9)
))


knitr::kable(
  head(tbl9[, 1:8], 10),
  caption = "First 10 rows (first 7 columns)"
)


```


