---
title: "New Correspondence Table"
output: rmarkdown::html_vignette

vignette: >
  %\VignetteIndexEntry{New Correspondence Table Function}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

This vignette provides information about using the New Correspondence Table function

This vignette provides information about applying the correspondenceTables package on the sample datasets included in it.


ATTENTION: please set as working directory a folder different than the folder in which the package has been installed, for instance as follows:

```{r}
library(correspondenceTables)
tmp_dir<-tempdir()
csv_files<-list.files(tmp_dir, pattern = ".csv")
if (length(csv_files)>0) unlink(csv_files)
```

LOCAL COPIES OF THE SAMPLE DATA

If users wish so, they can make copies of the sample datasets in a local folder of their choice. There are two ways of doing this:

1) Unpack into any folder of your choice the tar.gz file in which the package has arrived. All sample datasets may be found in the "inst/extdata" subfolder of this folder.

2) Copy sample datasets from the "extdata" subfolder of the folder in which the package has been installed in your PC's R library.


--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
Application of function newCorrespondenceTable().

The function fullPath is used in all cases in order to get the path of the required input files.

```{r}
fullPath <- function(CSVraw, CSVappended){
  NamesCsv <- system.file("extdata", CSVraw, package = "correspondenceTables")
  A <- read.csv(NamesCsv, header = FALSE, sep = ",")
   for (i in 1:nrow(A)) {
    for (j in 1:ncol(A)) {
      if (A[i,j]!="") {
        A[i, j] <- system.file("extdata", A[i, j], package = "correspondenceTables")
      }}}
  write.table(x = A, file = file.path(tmp_dir,CSVappended), row.names = FALSE, col.names = FALSE, sep = ",")
  return(A)
}
```

Case 1

```{r, results = "hide"}
fullPath("names1.csv", "names.csv")
```

Execute the following code to apply function newCorrespondenceTable() on these data. When no trimming is executed, redundant records are shown, together with the redundancy flag.

```{r, results = "hide"}
system.time(NCT <- newCorrespondenceTable(file.path(tmp_dir,"names.csv"), file.path(tmp_dir,"newCorrespondenceTableCase1.csv"), "A", 0.5, FALSE))
```

```{r}
print(NCT[[1]][1:10, 1:6])
print(NCT[[2]])
```

Case 2

```{r, results = "hide"}
fullPath("names2.csv", "names.csv")
```

Execute the following code to apply function newCorrespondenceTable() on these data. When no trimming is executed, redundant records are shown, together with the redundancy flag.

```{r, results = "hide"}
system.time(NCT <- newCorrespondenceTable(file.path(tmp_dir,"names.csv"), file.path(tmp_dir,"newCorrespondenceTableCase2.csv"), "B", 0.5, FALSE))
```

Case 3

```{r, results = "hide"}
fullPath("names3.csv", "names.csv")
```

Execute the following code to apply function newCorrespondenceTable() on these data. When there are redundant records, these are removed and kept exactly one record for each unique combination.

```{r, results = "hide"}
system.time(NCT <- newCorrespondenceTable(file.path(tmp_dir,"names.csv"), file.path(tmp_dir,"newCorrespondenceTableCase3.csv"), "B", 0.5, TRUE))
```

Case 4

```{r, results = "hide"}
fullPath("names4.csv", "names.csv")
```

Execute the following code to apply function newCorrespondenceTable() on these data. When there are redundant records, these are removed and kept exactly one record for each unique combination.

```{r, results = "hide"}
system.time(NCT <- newCorrespondenceTable(file.path(tmp_dir,"names.csv"), file.path(tmp_dir,"newCorrespondenceTableCase4.csv"), "none", 0.96, TRUE))
```

```{r message=TRUE, warning=TRUE, include=FALSE}
csv_files<-list.files(tmp_dir, pattern = ".csv")
if (length(csv_files)>0) unlink(csv_files)
```































