---
title: "Retrieve classification and correspondence tables with the correspondenceTables package"
output: rmarkdown::html_vignette

vignette: >
  %\VignetteIndexEntry{Retrieve classification and correspondence tables with the correspondenceTables package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

This vignette provides information about the functions included in the correspondenceTables package used to extract classification and correspondence tables from CELLAR and FAO endpoints.

```{r}
library(correspondenceTables)
```

The main two functions used to extract tables are retrieveClassificationTable() and retrieveCorrespondenceTable(), for classification and correspondence tables respectively. Other functions (prefixList(), classificationEndpoint(), dataStructure() and correspondenceList()) are used to understand the structure of each classification or correspondence table and retrieve information needed as input of the two main functions.

## Extract Classification Tables

The function retrieveClassificationTable() retrieves the classification table from the CELLAR and FAO repository, which can be used as an input to the newCorrespondenceTable and updateCorrespondenceTable functions. This function has five arguments: 

* prefix - the SPARQL instruction for a declaration of a namespace prefix
* endpoint - the SPARQL Endpoint: CELLAR or FAO
* conceptScheme - a unique identifier associated to specific classification table
* level - levels of the objects in the collection to be retrieved
* language - language of the table
* CSVout - preferred choice of output
* showQuery - the SPARQL query generated

The values of the prefix, conceptScheme and level can be found using the classificationEndpoint() and dataStructure() functions (see below).
The arguments level, language, CSVout and showQuery are optional and set as default as level="ALL", language="en", CSVout="FALSE" and showQuery="FALSE".

The namespace prefix needed to execute the SPARQL query are automatically generated using the prefixList() function (see below).

**Application of function retrieveClassificationTable()**

The following code is used to retrieve the NACE2 classification from CELLAR:

```{r, results = "hide"}
endpoint = "CELLAR"
# obtain prefix and conceptscheme using classificationEndpoint()
classificationEndpoint(endpoint)[[1]][,1:4]
prefix = "nace2"
conceptScheme = "nace2"
language = "en"
CSVout = FALSE
showQuery = TRUE

# identify lower level using dataStructure()
level_dt = dataStructure(prefix, conceptScheme, endpoint, language)
level = level_dt[nrow(level_dt),2] 
level_dt; level

result_ls = retrieveClassificationTable(prefix, endpoint, conceptScheme, level = level, language, CSVout, showQuery) 

# identify the SPARQL query used
SPARQLquery = result_ls[[1]]

# obtained the table
table = result_ls[[2]]

```


### Other functions used to extract Classification Tables

Following, the other functions used to extract the required information for the retrieveClassificationTable() function.

**Application of function prefixList()**

This function automatically obtains a list the prefixes from CELLAR and FAO used in the retrieveClassificationTable() and retrieveCorrespondenceTable() functions to retrieve the required tables. The list will be updated automatically each time a new classification or correspondence classification is introduced in CELLAR or FAO repository.

```{r, results = "hide"}
endpoint = "CELLAR"
prefixList(endpoint)
```

**Application of function classificationEndpoint()**

The function returns a table with information needed to retrieve the classification table:
\itemize{
    \item Prefix name: the  SPARQL instruction for a declaration of a namespace prefix
    \item Conceptscheme: a unique identifier associated to specific classification table
    \item URI: the URL from which the SPARQL query was retrieved
    \item Name: the name of the table retrieved
}

```{r, results = "hide"}
 endpoint = "ALL"
 list_data = classificationEndpoint(endpoint)
```


**Application of function dataStructure()**

Each classification has a different level based on their structure. The function dataStructure() retrieves information about the level names, their hierarchy and the numbers of records for all the classification available in the repositories (CELLAR and FAO). The level information needed as an optional arguments of the retrieveClassificationTable() function. 

The function returns a table with the following columns:        
\itemize{
     \item Concept_Scheme: a unique identifier associated to specific classification table
     \item Level: the levels of the objects in the collection
     \item Depth: identify the hierarchy of each level
     \item Count: the number of objects retrieved in each level
}

The following code produce a list including the structure of each classification available in CELLAR and FAO. 
```{r,results = "hide"}
## Obtain the structure of all classifications 
## CELLAR
data_CELLAR = list()
endpoint = "CELLAR"
#Get info to retrieve structure using classificationEndpoint()
list_data = classificationEndpoint("ALL")

#loop over all classification in CELLAR
for (i in 1:nrow(list_data$CELLAR)){
  prefix = list_data$CELLAR[i,1] 
  conceptScheme = list_data$CELLAR[i,2] 
  #language by default is English
  data_CELLAR[[i]] = dataStructure(prefix, conceptScheme, endpoint)
}
names(data_CELLAR) = list_data$CELLAR[,1] 

## FAO 
# data_FAO = list()
# endpoint = "FAO"
# for (i in 1:nrow(list_data$FAO)){
#   prefix = list_data$FAO[i,1]
#   conceptScheme = list_data$FAO[i,2] 
#   data_FAO[[i]] = dataStructure(prefix, conceptScheme, endpoint)
# }
# names(data_FAO) =  list_data$FAO[,1]
```

## Extract Correspondence Tables
The function retrieveCorrespondenceTable() retrieves the correspondences table from the CELLAR and FAO repository, which can be used as an input to the newCorrespondenceTable and updateCorrespondenceTable functions. This function has four arguments: 

* prefix - the SPARQL instruction for a declaration of a namespace prefix
* endpoint - the SPARQL Endpoint: CELLAR or FAO
* ID_table - the ID of the correspondence table
* language - language of the table
* CSVout - preferred choice of output
* showQuery - the SPARQL query generated

The values of the prefix and ID_table can be found using the correspondenceList() function (see below).
The argument language, CSVout and showQuery are optional and set as default as language="en", CSVout="FALSE" and showQuery="TRUE".

The namespace prefix needed to execute the SPARQL query are automatically generated using the prefixList() function (see above).

**Application of function retrieveCorrespondenceTable()**

To following code is used to retrieve the correspondence table between NACE2 and PRODCOM2021 from CELLAR:
```{r, results = "hide"}
endpoint = "CELLAR"
prefix = "nace2"
ID_table = "NACE2_PRODCOM2021"
language = "en"
CSVout = FALSE
showQuery= TRUE

result_ls = retrieveCorrespondenceTable(prefix, endpoint, ID_table, language, CSVout, showQuery)

# identify the SPARQL query used
SPARQLquery = result_ls[[1]]

# obtained the table
table = result_ls[[2]]
```

To following code is used to retrieve a specific correspondence table between CPCv21 and ISIC4 from FAO:
```{r, results = "hide"}
# endpoint = "FAO"
# prefix = "CPCv21"
# ID_table = "CPC21-ISIC4"
# language = "en"
# CSVout = FALSE
# showQuery= TRUE
# 
# result_ls = retrieveCorrespondenceTable(prefix, endpoint, ID_table, language, CSVout, showQuery)
# 
# # identify the SPARQL query used
# SPARQLquery = result_ls[[1]]
# 
# # obtained the table
# table = result_ls[[2]]
```

### Other functions used to extract Correspondence Tables
Following, the function used to extract the required information for the retrieveCorrespondenceTable() function.


**Application of function correspondenceList()**

The correspondenceList() provides an overview of all the available correspondence classification from CELLAR and FAO repository. 

```{r, message=FALSE, warning=FALSE, results = "hide"}
corr_list = correspondenceList("ALL")

#provides a table with all the correspondence tables for NACE2 in CELLAR
corr_list$CELLAR$`nace2:`

#provides a table with all the correspondence tables for CPC v21 in FAO
corr_list$FAO$`CPCv21:`
```

