---
title: "Retrieve classifications and correspondence tables stored as Linked Open Data"
output:
  rmarkdown::html_vignette:
    toc: TRUE

vignette: >
  %\VignetteIndexEntry{Retrieve classifications and correspondence tables stored as Linked Open Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---



```{r setup, include=FALSE}

knitr::opts_chunk$set(message = FALSE, warning = FALSE, fig.align = "center")
old <- getOption("useLocalDataForVignettes")
options(useLocalDataForVignettes = TRUE)
on.exit(options(useLocalDataForVignettes = old), add = TRUE)

```


## Overview  

Statistical classifications and correspondence tables are published as Linked Open Data (LOD) by several organisations, notably the Publications Office of the European Union (OP, via CELLAR) and the Food and Agriculture Organization (FAO).

While these resources can be accessed directly using SPARQL, this requires specific technical expertise. The **correspondenceTables** package provides high‑level R functions that allow users to retrieve these data as standard R data frames, without writing SPARQL queries themselves.

Two core retrieval functions are provided:

- `retrieveClassificationTable()`: retrieves the structure of a statistical
  classification (codes, labels, hierarchy).
- `retrieveCorrespondenceTable()`: retrieves a correspondence (mapping) table
  between two classifications.

Optionally, both functions can return the SPARQL query used for the retrieval, making the process transparent, inspectable, and reproducible.  

```{r}
library(correspondenceTables)
```


## Discovering available data

Before using the core retrieval functions
retrieveClassificationTable() and retrieveCorrespondenceTable(),
it is necessary to know what can be retrieved and how it is identified.
In practice, this means answering the following questions:

- Which classifications or correspondence tables are available?
- From which endpoint (CELLAR or FAO)?
- Which identifiers (prefix, conceptScheme, ID_table) should be used?
- For hierarchical classifications, which levels are available?

The package provides lightweight discovery utilities to support this step.

### Gathering information necessary for classification retrieval

To retrieve a statistical classification, users first need to know which
classifications are available at a given endpoint and how they are identified.
The `classificationList()` utility provides this information.

### Example 1: Available classifications (CELLAR)
The example below illustrates the typical output structure using a static
snapshot of the CELLAR classification list bundled with the package. To retrieve the updated information about the available classifications, the user just need to execute the `classificationList()` function, which will retrieve a data frame with all the available classification in a selected endpoint. 


```{r}
list_data <- read.csv(
  system.file("extdata", "classificationList_CELLAR.csv",
              package = "correspondenceTables"),
  stringsAsFactors = FALSE
)

knitr::kable(
  head(list_data, 3),
  caption = "Example output of classificationList()"
)

```
  

For each classification, three identifiers are required to retrieve the data:

- endpoint: "CELLAR" or "FAO"
- prefix: namespace prefix used in the SPARQL endpoint
- conceptScheme: unique identifier of the classification

For example, the NACE Rev. 2 classification:

- is available from the CELLAR repository,  
- uses prefix "nace2",
- uses concept scheme "nace2".

## Inspecting the structure of hierarchical classifications

Many statistical classifications are hierarchical.
If only a specific level is required (e.g. divisions or classes),
it is recommended to inspect the classification structure first.
The dataStructure() function provides this information.

### Example 2: Classification structure (NACE Rev. 2, CELLAR)

The following call illustrates how to inspect the structure of
NACE Rev. 2.
It is shown for documentation purposes and not executed during
vignette rendering to avoid reliance on live SPARQL endpoints.


Inspecting a classification structure from CELLAR (NACE Rev. 2)


```{r, eval = FALSE}

endpoint <- "CELLAR"
prefix <- "nace2"
conceptScheme <- "nace2"

ds <- dataStructure(
  endpoint = endpoint,
  prefix = prefix,
  conceptScheme = conceptScheme,
  language = "en",
  showQuery = FALSE
)

```


For **NACE Rev. 2**, four hierarchical levels are available:

1. Sections  
2. Divisions  
3. Groups  
4. Classes  

If the required level is already known, this inspection step can be skipped.


### Example 3: classification structure  (CPC2.1, FAO)

The same approach can be used for FAO classifications.  
The example below illustrates how to inspect the structure of **CPC2.1**.



```{r, eval = FALSE}
endpoint <- "FAO"
prefix <- "CPC21"
conceptScheme <- "CPC21"

ds_cpc <- dataStructure(
  endpoint = endpoint,
  prefix = prefix,
  conceptScheme = conceptScheme,
  language = "en",
  showQuery = FALSE
)

```


As with classifications retrieved from CELLAR, the output describes the hierarchical organisation of the classification and the levels available for retrieval.

If the required level is already known in advance, this inspection step can be skipped.


## Retrieving classification tables

Once the classification identifiers and (optionally) the desired level are known,
the `retrieveClassificationTable()` function can be used to retrieve the data.

The function returns a flat data frame suitable for:

- browsing and documentation;
- validation of codes and hierarchy;
- downstream correspondence analysis.

**Main arguments**

- `endpoint`: `"CELLAR"` or `"FAO"`
- `prefix`
- `conceptScheme`
- `language` (default: `"en"`)
- `level` (default: `"ALL"`)
- `showQuery` (logical)

### Example 4: Class‑level NACE Rev. 2 in multiple languages

The following example demonstrates how to retrieve level‑4 (“class”)
data for the German, French, and Bulgarian versions of **NACE Rev. 2**.
The code is **not executed** during vignette rendering.


```{r retrieve-nace-multilang, eval=FALSE}
endpoint <- "CELLAR"
prefix <- "nace2"
conceptScheme <- "nace2"
level <- "4"

languages <- c("de", "fr", "bg")

results <- lapply(languages, function(lang) {
  retrieveClassificationTable(
    endpoint = endpoint,
    prefix = prefix,
    conceptScheme = conceptScheme,
    language = lang,
    level = level,
    showQuery = FALSE
  )
})


```


### Example 5: FAO classification at group level

The FAO endpoint provides access to a limited subset of international classifications. Availability depends on the endpoint configuration.

The following example illustrates how a FAO classification *would* be retrieved. The code is not executed during vignette rendering.

This call queries the FAO repository and returns metadata describing all published classification schemes (prefix, concept scheme, title, etc.).

```{r, eval=FALSE}

cl_fao <- classificationList("FAO")

knitr::kable(
  head(cl_fao),
  caption = "Retrieving a classification table from the FAO endpoint"
)

```

 **Inspect available prefix identifiers**
 
 The Prefix field identifies the catalogue or namespace under which
 each FAO classification is published.

```{r, eval=FALSE}
knitr::kable(
  head(unique(cl_fao$Prefix)))
```

 **Inspect available concept schemes**
 
 The ConceptScheme field identifies the underlying classification schemes
 that can be queried using retrieveClassificationTable().

```{r, eval=FALSE}
knitr::kable(
  head(unique(cl_fao$ConceptScheme)))
```


### Retrieving a classification table from the FAO endpoint

The following example illustrates how to retrieve a classification from the FAO repository using retrieveClassificationTable().
Because FAO data availability and response times may vary, this example is shown for documentation purposes and is not executed in the vignette.


```{r retrieve-fao-classification, eval=FALSE}
endpoint <- "FAO"
prefix <- "cpc21"
conceptScheme <- "core"

out <- retrieveClassificationTable(
  endpoint      = endpoint,
  prefix        = prefix,
  conceptScheme = conceptScheme,
  language      = "en",
  level         = "2",
  showQuery     = TRUE
)
```


The FAO endpoint provides access to selected international and
domain‑specific classifications maintained by FAO.
Not all CELLAR classifications are available via FAO, and viceversa.



## Retrieving correspondence tables

**Gathering information necessary for correspondence table retrieval**

Before retrieving a correspondence table, users need to identify which correspondences are available and how they are referenced at a given SPARQL endpoint.
The `correspondenceTableList()` utility serves this purpose. It is analogous to `classificationList()`, but lists correspondence tables instead of classifications.

### Example 6: Available correspondence tables

The following example illustrates how to list correspondence tables available
from the CELLAR and FAO repositories.
It is shown for documentation purposes and not executed during vignette
rendering to avoid reliance on live external SPARQL endpoints.

```{r, eval = FALSE}

corr_list = correspondenceTableList("ALL")

names(corr_list)
#Correspondence tables available from CELLAR
knitr::kable(
  head(corr_list$CELLAR, 10),
  caption = "Available correspondence tables from the CELLAR endpoint (preview)"
)
#Correspondence tables available from FAO
knitr::kable(
  head(corr_list$FAO, 10),
  caption = "Available correspondence tables from the FAO endpoint (preview)"
)

```

When executed interactively, this call returns a list whose elements correspond
to the selected endpoints (e.g. `CELLAR`, `FAO`). Each element is a data frame
describing the available correspondence tables, including their identifiers,
associated prefixes, and human-readable labels.

Each correspondence table is identified by:

- **endpoint**: `"CELLAR"` or `"FAO"`
- **prefix**: namespace associated with the source classification
- **ID_table**: unique identifier of the correspondence table


**Retrieving correspondence tables**

The `retrieveCorrespondenceTable()` function retrieves a correspondence (mapping) table between two statistical classifications from a SPARQL endpoint. Its interface is similar to `retrieveClassificationTable()`, with the main difference that correspondence tables are identified using `ID_table` (instead of `conceptScheme`). Correspondence tables are usually provided at the
most granular level of the classifications involved.


### Inspect available correspondence tables (CELLAR)

The following examples illustrate how to inspect the correspondence tables
available from the CELLAR endpoints.

```{r corr-table-list, eval=FALSE}

# Inspect correspondence tables available from CELLAR
tbl_cellar <- correspondenceTableList("CELLAR")

#Correspondence tables available from CELLAR
knitr::kable(
  head(tbl_cellar, 10),
  caption = "Available correspondence tables from the CELLAR endpoint "
)


```


### Example 7: Retrieve a correspondence table from CELLAR
The following example illustrates the retrieval of a correspondence table published by the Publications Office of the European Union via the CELLAR endpoint.
Users should note that the availability of correspondence data depends on what is currently exposed by the underlying SPARQL endpoint. Although a correspondence table may be listed by `correspondenceTableList()`, it can legitimately return an empty result when queried. For some CELLAR correspondences (including several PRODCOM‑related mappings), `retrieveCorrespondenceTable()` may therefore return avalid but empty data frame, which does not indicate a failure of the retrieval
process.


```{r retrieve-prodcom, eval=FALSE}


res <- retrieveCorrespondenceTable(
  endpoint  = "CELLAR",
  prefix    = "prodcom2023",
  ID_table  = "PRODCOM2023_CPA21",
  language  = "en",
  showQuery = FALSE
)


knitr::kable(
  head(res, 10),
  caption = "PRODCOM2023_CPA21 CorrespondenceTable "
)
```



To reduce potential user confusion, it is helpful to include at least one
correspondence example that is more likely to return data when queried.


```{r, eval = FALSE}
res2 <- retrieveCorrespondenceTable(
  endpoint = "CELLAR",
  prefix   = "nace2",
  ID_table = "NACE2_CPA21",
  language = "en"
)


knitr::kable(
  head(res2, 10),
  caption = "NACE2_CPA21 CorrespondenceTable from the CELLAR endpoint "
)

```




For transparency and reproducibility, the SPARQL query used for retrieval can
also be inspected by setting `showQuery = TRUE`.


##Retrieve a correspondence table from FAO

### Inspect available correspondence tables (FAO)

The following examples illustrate how to inspect the correspondence tables
available from the FAO endpoints.

```{r, eval = FALSE}
# Inspect correspondence tables available from FAO
tbl_fao <- correspondenceTableList("FAO")
head(tbl_fao)

knitr::kable(
  head(tbl_fao, 10),
  caption = "correspondence tables available from FAO"
)


```

### Example 8: Retrieve a correspondence table from FAO: *CPC 2.1 : ISIC Rev. 4*

The following example illustrates the retrieval of a correspondence table published by the Food and Agriculture Organization of the United Nations (FAO) via the FAO endpoint.

Users should note that the availability of correspondence data depends on what is currently exposed by the underlying SPARQL endpoint. Although a correspondence table may be listed by `correspondenceTableList()`, it can legitimately return an empty result when queried. In practice, however, correspondence tables exposed by the FAO endpoint tend to be more consistently populated than some of those available from CELLAR.

The English-language version of the *CPC 2.1 : ISIC Rev. 4* correspondence table can be retrieved as follows. This example is not executed during vignette rendering.


```{r retrieve-cpc21-isic4_FAO , eval = FALSE}
Res <- retrieveCorrespondenceTable(
  endpoint = "FAO",
  prefix   = "CPC21",
  ID_table = "CPC21-ISIC4",
  language = "en"
)

knitr::kable(
  head(Res[, 1:5], 10),
  caption = "CPC21–ISIC4 correspondence tables available from FAO"
)
```

### (Optional) Inspect the underlying SPARQL query

For transparency and reproducibility, the SPARQL query used for retrieval can also be inspected by setting `showQuery = TRUE`.


```{r, eval = FALSE}
Res2 <- retrieveCorrespondenceTable(
  endpoint = "FAO",
  prefix   = "CPC21",
  ID_table = "CPC21-ISIC4",
  language = "en",
  showQuery = TRUE
)



# Extract the SPARQL query used
SPARQLquery <- Res2$SPARQL.query
SPARQLquery


```


## Summary   

The correspondenceTables package provides a consistent and transparent interface
to:

- discover available classifications and correspondence tables;
- retrieve them as standard R data frames;
- optionally inspect the underlying SPARQL queries used for retrieval.

This allows statisticians and data analysts to work with official classification systems and mappings without requiring SPARQL expertise, while preserving reproducibility and traceability.

