---
title: "Update Correspondence Table"
output: rmarkdown::html_vignette

vignette: >
  %\VignetteIndexEntry{Update Correspondence Table Function}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

This vignette provides information about using the Update Correspondence Table function

This vignette provides information about applying the correspondenceTables package on the sample datasets included in it.

ATTENTION: please set as working directory a folder different than the folder in which the package has been installed, for instance as follows:

```{r}
library(correspondenceTables)
tmp_dir<-tempdir()
csv_files<-list.files(tmp_dir, pattern = ".csv")
if (length(csv_files)>0) unlink(csv_files)
```

LOCAL COPIES OF THE SAMPLE DATA

If users wish so, they can make copies of the sample datasets in a local folder of their choice. There are two ways of doing this:

1) Unpack into any folder of your choice the tar.gz file in which the package has arrived. All sample datasets may be found in the "inst/extdata" subfolder of this folder.

2) Copy sample datasets from the "extdata" subfolder of the folder in which the package has been installed in your PC's R library.

--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------

ACCESSING SAMPLE DATASETS FROM WITHIN THE PACKAGE

Application of function updateCorrespondenceTable().

Case 1

Execute the following code in order to get the path of the required input files.

```{r}
A <- system.file("extdata", "CN2021.csv", package = "correspondenceTables")
AStar <- system.file("extdata", "CN2022.csv", package = "correspondenceTables")
B <- system.file("extdata", "CPA21.csv", package = "correspondenceTables")
AB <- system.file("extdata", "CN2021_CPA21.csv", package = "correspondenceTables")
AAStar <- system.file("extdata", "CN2021_CN2022.csv", package = "correspondenceTables")
```

Execute the following code line to apply function updateCorrespondenceTable() on these data. When there are redundant records, these are removed and kept exactly one record for each unique combination.

```{r}
UPC <- updateCorrespondenceTable(A, B, AStar, AB, AAStar, file.path(tmp_dir,"updateCorrespondenceTableCase1.csv"),
                                 "B", 0.4, 0.4, TRUE)
print(UPC[[1]][1:10, 1:7])
print(UPC[[2]])
```

Case 2

Execute the following code in order to get the path of the required input files.

```{r}
A <- system.file("extdata", "CN2021.csv", package = "correspondenceTables")
AStar <- system.file("extdata", "CN2022.csv", package = "correspondenceTables")
B <- system.file("extdata", "PRODCOM2021.csv", package = "correspondenceTables")
AB <- system.file("extdata", "CN2021_PRODCOM2021.csv", package = "correspondenceTables")
AAStar <- system.file("extdata", "CN2021_CN2022.csv", package = "correspondenceTables")
```

Execute the following code line to apply function updateCorrespondenceTable() on these data. When there are redundant records, these are removed and kept exactly one record for each unique combination.

```{r, results = "hide"}
UPC <- updateCorrespondenceTable(A, B, AStar, AB, AAStar, file.path(tmp_dir,"updateCorrespondenceTableCase2.csv"), "A", 0.4, 0.3, TRUE)
```

Case 3

Execute the following code in order to get the path of the required input files. 

```{r}
A <- system.file("extdata", "NAICS2017.csv", package = "correspondenceTables")
AStar <- system.file("extdata", "NAICS2022.csv", package = "correspondenceTables")
B <- system.file("extdata", "NACE.csv", package = "correspondenceTables")
AB <- system.file("extdata", "NAICS2017_NACE.csv", package = "correspondenceTables")
AAStar <- system.file("extdata", "NAICS2017_NAICS2022.csv", package = "correspondenceTables")
```

Execute the following code line to apply function updateCorrespondenceTable() on these data. When there are redundant records, these are removed and kept exactly one record for each unique combination.

```{r, results = "hide"}
UPC <- updateCorrespondenceTable(A, B, AStar, AB, AAStar, file.path(tmp_dir,"updateCorrespondenceTableCase3.csv"), "none", 0.5, 0.3, TRUE)
```

Case 4

Execute the following code in order to get the path of the required input files.

```{r}
A <- system.file("extdata", "CN2021.csv", package = "correspondenceTables")
AStar <- system.file("extdata", "CN2022.csv", package = "correspondenceTables")
B <- system.file("extdata", "NST2007.csv", package = "correspondenceTables")
AB <- system.file("extdata", "CN2021_NST2007.csv", package = "correspondenceTables")
AAStar <- system.file("extdata", "CN2021_CN2022.csv", package = "correspondenceTables")
```

Execute the following code line to apply function updateCorrespondenceTable() on these data. When no trimming is executed, redundant records are shown, together with the redundancy flag.

```{r, results = "hide"}
UPC <- updateCorrespondenceTable(A, B, AStar, AB, AAStar, file.path(tmp_dir,"updateCorrespondenceTableCase4.csv"), "B", 0.4, 0.3, TRUE)
```

Case 5

Execute the following code in order to get the path of the required input files. 

```{r}
A <- system.file("extdata", "CN2021.csv", package = "correspondenceTables")
AStar <- system.file("extdata", "CN2022.csv", package = "correspondenceTables")
B <- system.file("extdata", "SITC4.csv", package = "correspondenceTables")
AB <- system.file("extdata", "CN2021_SITC4.csv", package = "correspondenceTables")
AAStar <- system.file("extdata", "CN2021_CN2022.csv", package = "correspondenceTables")
```

Execute the following code line to apply function updateCorrespondenceTable() on these data. When no trimming is executed, redundant records are shown, together with the redundancy flag.

```{r, results = "hide"}
UPC <- updateCorrespondenceTable(A, B, AStar, AB, AAStar, file.path(tmp_dir,"updateCorrespondenceTableCase5.csv"), "B", 0.3, 0.7, TRUE)
```

Case 6

Execute the following code in order to get the path of the required input files.

```{r}
A <- system.file("extdata", "CN2021.csv", package = "correspondenceTables")
AStar <- system.file("extdata", "CN2022.csv", package = "correspondenceTables")
B <- system.file("extdata", "BEC4.csv", package = "correspondenceTables")
AB <- system.file("extdata", "CN2021_BEC4.csv", package = "correspondenceTables")
AAStar <- system.file("extdata", "CN2021_CN2022.csv", package = "correspondenceTables")
```

Execute the following code line to apply function updateCorrespondenceTable() on these data. When no trimming is executed, redundant records are shown, together with the redundancy flag.

```{r, results = "hide"}
UPC <- updateCorrespondenceTable(A, B, AStar, AB, AAStar, file.path(tmp_dir,"updateCorrespondenceTableCase6.csv"), "B", 0.3, 0.6, FALSE)
```
































