---
title: "Utility Functions for retrieving classifications and correspondence tables"
output: rmarkdown::html_vignette

vignette: >
  %\VignetteIndexEntry{Utility Functions for retrieving classifications and correspondence tables}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

Get structural information necessary for retrieving classifications and correspondence tables that are stored as Linked Open Data

```{r}
library(correspondenceTables)
```

In order to be able to retrieve classifications or correspondence tables using the retrieveClassification or retrieveCorrespondenceTable functions, users need to know where to look for these data – and what information is available there. To this end, the utility function classificationEndpoint has been developed to list available endpoints, and a range of utility functions (prefixList, dataStructure and correspondenceList) have been developed to list the relevant classification (and correspondence table) information available at each endpoint. 


### Utility functions used to extract Classification and Correspondence Tables 


**Application of function prefixList()**

This function automatically obtains a list the prefixes from CELLAR and FAO used in the retrieveClassificationTable() and retrieveCorrespondenceTable() functions to retrieve the required tables. The list will be updated automatically each time a new classification or correspondence classification is introduced in CELLAR or FAO repository. Please un-comment function before running for dynamic data.

```{r, results = "hide"}
endpoint = "CELLAR"
#prefixList(endpoint)
```

**Application of function classificationEndpoint()**

The function returns a table with information needed to retrieve the classification table:
\itemize{
    \item Prefix name: the  SPARQL instruction for a declaration of a namespace prefix
    \item Conceptscheme: a unique identifier associated to specific classification table
    \item URI: the URL from which the SPARQL query was retrieved
    \item Name: the name of the table retrieved
}

```{r, results = "hide"}
 endpoint = "ALL"
 #list_data = classificationEndpoint(endpoint)
```


**Application of function dataStructure()**

Each classification has a different level based on their structure. The function dataStructure() retrieves information about the level names, their hierarchy and the numbers of records for all the classification available in the repositories (CELLAR and FAO). The level information needed as an optional arguments of the retrieveClassificationTable() function. 

The function returns a table with the following columns:        
\itemize{
     \item Concept_Scheme: a unique identifier associated to specific classification table
     \item Level: the levels of the objects in the collection
     \item Depth: identify the hierarchy of each level
     \item Count: the number of objects retrieved in each level
}

The following code produce a list including the structure of each classification available in CELLAR and FAO. 
Please un-comment code before running for dynamic data.
```{r,results = "hide"}
## Obtain the structure of all classifications 
## CELLAR
# data_CELLAR = list()
# endpoint = "CELLAR"
# #Get info to retrieve structure using classificationEndpoint()
# list_data = classificationEndpoint("ALL")

# #loop over all classification in CELLAR
# for (i in 1:nrow(list_data$CELLAR)){
#   prefix = list_data$CELLAR[i,1] 
#   conceptScheme = list_data$CELLAR[i,2] 
#   #language by default is English
#   data_CELLAR[[i]] = dataStructure(prefix, conceptScheme, endpoint)
# }
# names(data_CELLAR) = list_data$CELLAR[,1] 

## FAO 
# data_FAO = list()
# endpoint = "FAO"
# for (i in 1:nrow(list_data$FAO)){
#   prefix = list_data$FAO[i,1]
#   conceptScheme = list_data$FAO[i,2] 
#   data_FAO[[i]] = dataStructure(prefix, conceptScheme, endpoint)
# }
# names(data_FAO) =  list_data$FAO[,1]
```


**Application of function correspondenceList()**

The correspondenceList() provides an overview of all the available correspondence classification from CELLAR and FAO repository. 

```{r, message=FALSE, warning=FALSE, results = "hide"}
#corr_list = correspondenceList("ALL")

#provides a table with all the correspondence tables for NACE2 in CELLAR
#corr_list$CELLAR$`nace2:`

#provides a table with all the correspondence tables for CPC v21 in FAO
# corr_list$FAO$`CPCv21:`
```

