---
title: "Vignette_Classification Quality Control"
output: rmarkdown::html_vignette


vignette: >
  %\VignetteIndexEntry{Retrieve classification quality control with the correspondenceTables package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

This vignette provides information about the functions included in the correspondenceTables package used to create a quality control of the classification

```{r}
library(correspondenceTables)
```


The main function `classificationQC()` function is designed for hierarchical classifications but is adaptable for flat classifications. It does not process the specialized terminological rules of certain categories, such as 'other' and 'not elsewhere classified,' due to language-specific variations. However, it facilitates the extraction of these categories for potential post-processing by a classifications analyst. The function return a dataframe for analysis. 

 This function has eight arguments :
* classification - containing the name of a CSV file of the classification provided by the user.
* lenghtsfile -  The user provide a csv file the different level of hierarchical classification.    
* fullHierarchy - This rule outlines criteria for assessing the completeness If fullHierarchy is FALSE, the rule applies to positions at hierarchical levels greater than 1. If fullHierarchy is TRUE, a second rule is tested.
* labelUniqueness - This rule define is there is in our classification any duplicates
* labelHierarchy - This rule define a new column depending on the children label in relation to the parents.
* singleChildCode - The user provide a csv file in order to create two new columns singleCodeError multipleCodeError  
* sequencing - The user provide a csv file in order to create a nerw column Sequencing 
* CSVout - preferred choice of output


**Requirement for the csv file for LenghtsFile, singleChildCode, sequencing**

**LenghtsFile** the user provide a csv file with these headers **charb chare**
if not return a warning message that there is not these headears and will be corrected.

**SingleChildCode** the user provide a csv with these headers **level,singleCode,multipleCode** If this is not the case, then the function will return a warning saying that the headers are wrong and will correct them to set the correct ones 

**Sequencing** had the same logic like SingleChildCode but his headers are different : **level  multipleCode**

Here we load the different  csv file in order to see the column for the next example with error on the headers
```{r, results = "hide"}
lengthsFile <- read.csv( system.file("extdata", "lenghtsNaceNoColumn.csv", package = "correspondenceTables"))
## Here lenghtsFile has no column
colnames(lengthsFile)
singleChildCode <- read.csv(system.file("extdata","SingleChild.csv", package = "correspondenceTables"))
# SingleChildCode has the good column
colnames(singleChildCode)
sequencing <- read.csv(system.file("extdata","Sequencing.csv", package = "correspondenceTables"))
#Sequencing has string as a column it will be replaced see next chunk 
colnames(sequencing)


```


**Application of the function classificationQC()**

The following code is used to create the quality control of the NACE2 classification from CELLAR:
Here we used different parameters :

The user provide a csv file for Classification and lengthsFile. 

```{r, results = "hide"}
output <- classificationQC(classification = system.file("extdata", "Nace2.csv", package ="correspondenceTables"),
                             lengthsFile = system.file("extdata", "lenghtsNace.csv", package = "correspondenceTables"),
                             fullHierarchy = TRUE,
                             labelUniqueness  = TRUE, labelHierarchy = TRUE,
                             singleChildCode = NULL, sequencing = NULL,
                             CSVout = NULL) 


output$QC_output
```

**Full hierarchy** If fullHierarchy is FALSE, the rule applies to positions at hierarchical levels greater than 1.
A new field in the QC output, named "orphan," takes the value 1 for positions lacking a parent at the immediately higher hierarchical level (j-1) (otherwise 0).
Positions Above Level k (j < k):

If fullHierarchy is TRUE, a second rule is tested.
A new field in the QC output, named "childless," takes the value 1 for positions at hierarchical level j lacking a child at the immediately lower hierarchical level (j+1) (otherwise 0).

The **labelUniqueness** argument (default value: TRUE) indicates whether compliance with this rule is to be tested.
The test outcome is reported in a new 'QC output' column (duplicateLabel), assuming the value 1 for positions involved in duplicates and 0 otherwise.


The **labelHierarchy** argument (default value: TRUE) is used to indicate whether compliance with this rule is to be tested.
The test outcome is reported in a new 'QC output' column (singleChildMismatch) for each hierarchical level j > 1 (with a blank value for j = 1, i.e., at the highest hierarchical level).
Value 1 is assumed for single children having labels not matching that of their parent.
Value 9 is assumed for children having labels matching that of their parent without being a single child.
Otherwise, the value is assumed to be 0.

**Application of an another example of the function classificationQC()**

For this example the different  CSV File have wrong headers in the output we got warning messages.

The following code is used to create the quality control of the NACE2 classification from CELLAR:
Here we used different parameters and we had SingleChildCode :

```{r, results = "hide"}
output2 <-  classificationQC(
            classification = system.file("extdata", "Nace2.csv", package ="correspondenceTables"),
            lengthsFile = system.file("extdata", "lenghtsNaceNoColumn.csv", package = "correspondenceTables"),
            fullHierarchy = TRUE,
            labelUniqueness  = TRUE,
            labelHierarchy = TRUE,
            singleChildCode = system.file("extdata","SingleChild.csv", package = "correspondenceTables"),            
            sequencing = NULL,
            CSVout = NULL)

output2$QC_multipleCodeError
output2$QC_output

```



**Last application of an another example of the function classificationQC()**

We used here the parameter **sequencing** for our last example sequencing will be used on the level 3 and 4 here.

```{r, results = "hide"}
output3 <-  classificationQC(
            classification = system.file("extdata", "Nace2.csv", package ="correspondenceTables"),
            lengthsFile = system.file("extdata", "lenghtsNaceNoColumn.csv", package = "correspondenceTables"),
            fullHierarchy = TRUE,
            labelUniqueness  = TRUE,
            labelHierarchy = TRUE,
            singleChildCode = system.file("extdata","SingleChild2.csv", package = "correspondenceTables"),
            sequencing = c(3,4),
            CSVout = NULL)

output3$QC_output
output3$QC_lastSibling
```

