---
title: "analyseCorrespondenceTable"
author: "Clément Thomas"
date: "2023-09-21"
output: html_document
description: "This vignette explains how to use the analyseCorrespondenceTable function."
---

## Description

This vignette explains how to use the `analyseCorrespondenceTable` function to perform analysis on correspondence tables.

### Package Installation

To use the `analyseCorrespondenceTable` function, you first need to install and load the `correspondenceTables` package. You can do so using the following command:

```{r}
# Install the package from CRAN
library(correspondenceTables)
```

```{r}
# Load correspondence table data
AB_path <- system.file("extdata", "ExempleAnnexe.csv", package = "correspondenceTables")
AB <- read.csv(AB_path)

# Perform analysis
result <- analyseCorrespondenceTable(AB, A = NULL, formatA = NULL, B = NULL, formatB = NULL,
                                     CSVcorrespondenceInventory = NULL, CSVcorrespondenceAnalysis = NULL)

# Print the results
print(result$Annexe_A)
print(result$Annexe_B)

```

For this example we don't create  any output because **CSVcorrespondenceInventory** **CSVcorrespondenceAnalysis** are null but we can see these with the both print on this function.


## Example with an output as CSV : 

```{r}
AB_path <- system.file("extdata", "ExempleAnnexe.csv", package = "correspondenceTables")
AB <- read.csv(AB_path)

# Perform analysis
result <- analyseCorrespondenceTable(AB, A = NULL, formatA = NULL, B = NULL, formatB = NULL,
                                     CSVcorrespondenceInventory = TRUE, CSVcorrespondenceAnalysis = NULL)

# Print the results
print(result$Annexe_A)
print(result$Annexe_B)
```

For this example the user use **CSVcorrespondenceInventory** as TRUE so he will create a csv with correspondence Inventory as a result. 



