---
title: "analyseCorrespondenceTable"
author: "Clément Thomas"
date: "2023-09-21"
output: html_document
description: "This vignette explains how to use the analyseCorrespondenceTable function."
---

## Description

This vignette explains how to use the `analyseCorrespondenceTable` function to perform analysis on correspondence tables.

### Package Installation

To use the `analyseCorrespondenceTable` function, you first need to install and load the `correspondenceTables` package. You can do so using the following command:

```{r}
# Install the package from CRAN
library(correspondenceTables)
```

```{r}
# Load correspondence table data
AB_path <- system.file("extdata", "ExempleAnnexe.csv", package = "correspondenceTables")
AB <- read.csv(AB_path)

# Perform analysis
result <- analyseCorrespondenceTable(AB, A = NULL, formatA = NULL, B = NULL, formatB = NULL,
                                     CSVcorrespondenceInventory = NULL, CSVcorrespondenceAnalysis = NULL)

# Print the results
print(result$Annexe_A)
print(result$Annexe_B)

```

For this example we don't create  any output because **CSVcorrespondenceInventory** **CSVcorrespondenceAnalysis** are null but we can see these with the both print on this function.


But if the user want an output  of it work he had to change these variable in *TRUE* 



