---
title: "CorrectionClassification"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CorrectionClassification & LengthsFile}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Introduction
This vignette provides information about the functions correctionClassification and lengthsFile included in the correspondenceTables package. These functions are designed to assist in retrieving classification tables from CELLAR and FAO repositories.
```{r}
library(correspondenceTables)
```


**CorrectionClassification Function**

The correctionClassification function is used to correct the classification codes based on specific rules for each classification. It takes the following parameter:

Classification - Code name (e.g. nace2): the code of each object
Classification Label - corresponding name of each object


**Application of function CorrectionClassification **

To following code is used to corrects the classification table by adding necessary prefixes or removing unwanted characters.
```{r}
prefix = "nace2"
conceptScheme = "nace2"
endpoint = "CELLAR"
language = "en"
options(useLocalDataForVignettes = TRUE)
classification = retrieveClassificationTable(prefix,endpoint,conceptScheme,language="en",level="ALL")
colnames(classification)[1:2] = c("Code", "Label")
classification
```

These different code show the different correction for each classification.

**Correction for (NACE - NACE 2.1 - CPA21 - and ISIC) add a letter **
Letter addition for NACE, NACE 2.1, CPA21, and ISIC:
 
For each classification (NACE, NACE 2.1, CPA21, and ISIC), specific code ranges are identified using the substr function. Then, a letter is added to the corresponding code values in the classification$Code column. For example, codes starting with "01" or "02" or "03" are assigned the letter "A", codes starting with "05" or "06" or "07" or "08" or "09" are assigned the letter "B" and for the other number we input different letters from alphabet 
```{r}
   if (prefix %in% c("nace2", "nace21", "cpa21", "ISICrev4")) {
        A_code = which(substr(classification$Code, 1, 2) %in% c("01", "02", "03"))
        classification$Code[A_code] = paste0("A", classification$Code[A_code])
        B_code = which(substr(classification$Code, 1, 2) %in% c("05", "06", "07", "08", "09"))
        classification$Code[B_code] = paste0("B", classification$Code[B_code])
        C_code = which(substr(classification$Code, 1, 2) %in% c("10", "11", "12", "13", "14", "15", "16", "17", "18", "19", "20", 
                                                                "21", "22", "23", "24", "25", "26", "27", "28", "29", "30", "31", "32", "33"))
        classification$Code[C_code] = paste0("C", classification$Code[C_code])
        D_code = which(substr(classification$Code, 1, 2) %in% c("35"))
        classification$Code[D_code] = paste0("D", classification$Code[D_code])
        E_code = which(substr(classification$Code, 1, 2) %in% c("36", "37", "38", "39"))
        classification$Code[E_code] = paste0("E", classification$Code[E_code])
        F_code = which(substr(classification$Code, 1, 2) %in% c("41", "42", "43"))
        classification$Code[F_code] = paste0("F", classification$Code[F_code])
        G_code = which(substr(classification$Code, 1, 2) %in% c("45", "46", "47"))
        classification$Code[G_code] = paste0("G", classification$Code[G_code])
        H_code = which(substr(classification$Code, 1, 2) %in% c("49", "50", "51", "52", "53"))
        classification$Code[H_code] = paste0("H", classification$Code[H_code])
        I_code = which(substr(classification$Code, 1, 2) %in% c("55", "56"))
        classification$Code[I_code] = paste0("I", classification$Code[I_code])
        J_code = which(substr(classification$Code, 1, 2) %in% c("58", "59", "60", "61", "62", "63"))
        classification$Code[J_code] = paste0("J", classification$Code[J_code])
        K_code = which(substr(classification$Code, 1, 2) %in% c("64", "65", "66"))
        classification$Code[K_code] = paste0("K", classification$Code[K_code])
        L_code = which(substr(classification$Code, 1, 2) %in% c("68"))
        classification$Code[L_code] = paste0("L", classification$Code[L_code])
        M_code = which(substr(classification$Code, 1, 2) %in% c("69", "70", "71", "72", "73", "74", "75"))
        classification$Code[M_code] = paste0("M", classification$Code[M_code])
        N_code = which(substr(classification$Code, 1, 2) %in% c("77", "78", "79", "80", "81", "82"))
        classification$Code[N_code] = paste0("N", classification$Code[N_code])
        O_code = which(substr(classification$Code, 1, 2) %in% c("84"))
        classification$Code[O_code] = paste0("O", classification$Code[O_code])
        P_code = which(substr(classification$Code, 1, 2) %in% c("85"))
        classification$Code[P_code] = paste0("P", classification$Code[P_code])
        Q_code = which(substr(classification$Code, 1, 2) %in% c("86", "87", "88"))
        classification$Code[Q_code] = paste0("Q", classification$Code[Q_code])
        R_code = which(substr(classification$Code, 1, 2) %in% c("90", "91", "92", "93"))
        classification$Code[R_code] = paste0("R", classification$Code[R_code])
        S_code = which(substr(classification$Code, 1, 2) %in% c("94", "95", "96"))
        classification$Code[S_code] = paste0("S", classification$Code[S_code])
        T_code = which(substr(classification$Code, 1, 2) %in% c("97", "98"))
        classification$Code[T_code] = paste0("T", classification$Code[T_code])
        U_code = which(substr(classification$Code, 1, 2) %in% c("99"))
        classification$Code[U_code] = paste0("U", classification$Code[U_code])
    }
```


**Remove .0 for 10, 11 and 12 division for ecoicop**


If the prefix is "ecoicop" and the code values in the classification$Code column are "10.0", "11.0", or "12.0", they are replaced with "10", "11", and "12", respectively.
```{r}
  if (prefix %in% c("ecoicop")) {
        level1_code = which(classification$Code %in% c("10.0", "11.0", "12.0"))
        classification$Code[level1_code] = c("10", "11", "12") 
    }
    
```

**remove weird code 00.99.t and 00.99.t for prodcom2019**      

Remove weird codes for prodcom2019:

If the prefix is "prodcom2019" and the code values in the classification$Code column are "00.99.t" or "00.99.z", those rows are removed from the classification data frame.
```{r}
   
    if (prefix %in% c("prodcom2019")) {
        level1_code = which(classification$Code %in% c("00.99.t", "00.99.z"))
        classification = classification[-level1_code,]
    }
    
```

**remove section for CN**

If the prefix is one of "cn2017", "cn2018", "cn2019", "cn2020", "cn2021", "cn2021", "cn2022", or "cn2023", sections are identified based on the presence of alphabetic characters in the classification Code column n. Rows containing sections are then removed from the classification data frame.s
```{r}
  if (prefix %in% c("cn2017", "cn2018", "cn2019", "cn2020", "cn2021", "cn2021", "cn2022", "cn2023")) {
        level1_code = which(gsub("[^a-zA-Z]", "", classification$Code)!= "")
        if (length(level1_code)> 0){
          classification = classification[-level1_code,]
        }
    }
```

**remove "." in the end of the code for CBF**

If the prefix is "cbf10",  the last character (".") is removed from the code values in the classification Code column.
```{r}
if (prefix %in% c("cbf10")) {
        classification[,1] = substr(classification[,1], 1, nchar(classification[,1])-1)
    }
```
