---
title: "Vignette_Aggregate_CorrespondenceTable"
output: html_document


vignette: >
  %\VignetteIndexEntry{Aggregate classification between A & B  with the correspondenceTables package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This vignette provides information about the functions included in the correspondenceTables package used to create an aggregation between two classifications

Load the package correspondenceTables : 
```{r cars}
library(correspondenceTables)
```

The `aggregateCorrespondenceTable` function in R is designed to aggregate correspondence tables between two hierarchical classifications. It facilitates the process of expressing statistics compiled at different levels in classification A to corresponding levels in  classification B. The function output is mechanically defined and provides candidate  aggregations for subsequent analysis by statistical classification experts.
 
The function expects three mandatory CSV files (AB, A, and B) as input. The structure of these files is crucial.
 
- **AB**: Input correspondence table
- **A**: Source classification table
- **B**: Target classification table
- **CSVOUT** Retrieve the result as a csv


**Application of the aggregateCorrespondenceTable()**

```{r, results = "hide"}
 AB <- (system.file("extdata", "ab_data.csv", package = "correspondenceTables"))
 A <- (system.file("extdata", "a_data.csv", package = "correspondenceTables"))
 B <- (system.file("extdata", "b_data.csv", package = "correspondenceTables"))

 
 result <- aggregateCorrespondenceTable(AB = AB, A = A, B = B, CSVout = FALSE)
 
 print(result)

```

**Other Example** 

```{r, results = "hide"}

 AB <- (system.file("extdata", "ab_data.csv", package = "correspondenceTables"))
 A <- (system.file("extdata", "a_data.csv", package = "correspondenceTables"))
 B <- (system.file("extdata", "b_data.csv", package = "correspondenceTables"))

 
 result <- aggregateCorrespondenceTable(AB = AB, A = A, B = B, CSVout = TRUE)
 
 print(result)
```

