---
title: "AnalyseCorrespondenceTable"
description: "This vignette explains how to use the analyseCorrespondenceTable function."
vignette: >
  %\VignetteIndexEntry{Analyse classification   correspondence tables with the correspondenceTables package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Description

This vignette explains how to use the `analyseCorrespondenceTable` function to perform analysis on correspondence tables.

### Package Installation

To use the `analyseCorrespondenceTable` function, you first need to install and load the `correspondenceTables` package. You can do so using the following command:

```{r include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

```{r}
library(correspondenceTables)
```

```{r}
# Load correspondence table data
AB_path <- system.file("extdata", "ExempleAnnexe.csv", package = "correspondenceTables")
AB <- read.csv(AB_path)

# Perform analysis
result <- analyseCorrespondenceTable(AB =read.csv(system.file("extdata", "ExempleAnnexe.csv", package = "correspondenceTables"))
                                     , A = NULL, formatA = NULL, B = NULL, formatB = NULL,
                                     CSVcorrespondenceInventory =system.file("extdata", "CorrespondenceInventoryExample.csv", package = "correspondenceTables")
                                     , CSVcorrespondenceAnalysis = system.file("extdata", "CorrespondenceAnalysisExample.csv", package = "correspondenceTables"))

# Print the results
print(result$Annexe_A)
print(result$Annexe_B)

```

For this example we use output  **CSVcorrespondenceInventory** **CSVcorrespondenceAnalysis** are not null Indeed we put our output in these csv files and we can see these with the both print on this function.



